Deep Learning

### 2015-01-12 deepreview.tex
added the caption generation citations

When LSTMs were first described % in English
\citep{Hochreiter+Schmidhuber-1997} their complexity was off-putting
and, despite their impressive ability to learn very long-range temporal
structure on toy problems, they were largely ignored until they achieved
excellent results in a competition to read cursive
hand-writing~\citep{Graves-et-al-2009}. They have subsequently proved to be very
effective for tasks that have sequential input.  They are now better than
deep feed-forward networks for speech recognition~\citep{gravestimit} and
unlike feed-forward nets they can implement an entire speech recognition
system that goes all the way from coefficents derived from the soundwave to
the sequence of characters in the transcription~\citep{gravestimit}.  They
are also what is currently used for the encoder and decoder networks that
perform so well at machine
translation~\citep{Bahdanau-et-al-arxiv2014,Sutskever-et-al-NIPS2014}.

@@

When translating between languages, the hidden units of the decoder network
that generates possible translations are conditioned on (i.e., receive as extra
input or as initialization) a ``thought
vector'' which is the final hidden state of an encoder network.  But it is
also possible to initialize a decoder network using a linear transformation
of the last hidden layer of a deep convolutonal network that has already
been trained to recognize objects in images. The decoder network can then
be trained by BPTT on a dataset of captioned
images~\citep{NIC,StanfordNIC,more?} and it produces remarkably good
captions (see Figure~\ref{fig:caption-generation}).

@@

Similarly, instead of translating the meaning of a French sentence to an English sentence,
one can learn to ``translate'' the meaning of an image into an English sentence,
as illustrated in Figure~\ref{fig:caption-generation}. The ``encoder'' here is
a convolutional neural network (see below), a deep architecture that is particularly
well suited to extract a meaningful representation from an image, while the ``decoder''
is a recurrent neural network similar to the ones used for machine translation
and neural language modeling. There has been a surge of interest in such
systems recently~\citep{Vinyals-et-al-arxiv2014,OTHER-CAPTION-GENERATION-PAPERS}.

>>>>

When LSTMs were first described % in English
\citep{Hochreiter+Schmidhuber-1997} their complexity was off-putting
and, despite their impressive ability to learn very long-range temporal
structure on toy problems, they were largely ignored until they achieved
excellent results in a competition to read cursive
hand-writing~\citep{Graves-et-al-2009}. They have subsequently proved to be very
effective for tasks that have sequential input.  They are now better than
deep feed-forward networks for speech recognition~\citep{Graves-et-al-ICASSP2013} and
unlike feed-forward nets they can implement an entire speech recognition
system that goes all the way from coefficents derived from the soundwave to
the sequence of characters in the transcription~\citep{gravestimit}.  They
are also what is currently used for the encoder and decoder networks that
perform so well at machine
translation~\citep{Bahdanau-et-al-arxiv2014,Sutskever-et-al-NIPS2014}.

@@

When translating between languages, the hidden units of the decoder network
that generates possible translations are conditioned on (i.e., receive as extra
input or as initialization) a ``thought
vector'' which is the final hidden state of an encoder network.  But it is
also possible to initialize a decoder network using a linear transformation
of the last hidden layer of a deep convolutonal network that has already
been trained to recognize objects in images. The decoder network can then
be trained by BPTT on a dataset of captioned
images~\citep{Kiros-et-al-ICML2014,Mao+al-arxiv2014,Donahue-et-al-arxiv2014,
              Vinyals-et-al-arxiv2014,
             Chen+Zitnick-arxiv2014,Karpathy+Li-arxiv2014,Venugopalan-et-al-arxiv2014} 
and such models produce remarkably good
captions (see Figure~\ref{fig:caption-generation}).

@@

Similarly, instead of translating the meaning of a French sentence to an English sentence,
one can learn to ``translate'' the meaning of an image into an English sentence,
as illustrated in Figure~\ref{fig:caption-generation}. The ``encoder'' here is
a convolutional neural network (see below), a deep architecture that is particularly
well suited to extract a meaningful representation from an image, while the ``decoder''
is a recurrent neural network similar to the ones used for machine translation
and neural language modeling. There has been a surge of interest in such
systems recently~\citep{Kiros-et-al-ICML2014,Mao+al-arxiv2014,Donahue-et-al-arxiv2014,
              Vinyals-et-al-arxiv2014,Fang-et-al-arxiv2014,
             Chen+Zitnick-arxiv2014,Karpathy+Li-arxiv2014,Venugopalan-et-al-arxiv2014}.
